Estudio variabilidad estructural proteica

### 2016-09-16 OUT/analysis-structure-CA.Rmd
cambios 16/09/2016

---
title: "Structural Divergence Analysis"
author: "María Laura Marcos, Julian Echave"
date: "25 de julio de 2016"
output: html_document
---

@@

setwd("C:/Users/Usuario/Desktop/VariabilidadEstructuralProteica")

source("OUT/out_subset_CA/multiplot.R")
source("OUT/out_subset_CA/my-functions.R")
```

```{r set_my_colors, eval = T}
myColors = c("blue", "darkgreen", "red", "red")
names(myColors) <- c("exp", "mut", "strong", "mut+sel")

setwd("C:/Users/Usuario/Desktop/VariabilidadEstructuralProteica/OUT")

```
# Introduction
We study the evolutionary divergence of proteins using the LFENM and compare with experimental data.

```{r set_run_variables}
# Set options
family = "globins"
R0 = 10
enm = "ANM"

# significance factors
f95 = 1.96
f99 = 2.6
f999 = 3.3
data.dir = paste("out_subset_CA", sep = "")
```

@@

reference.fname = file.path(data.dir, paste(family, "_ref.txt", sep = ""))
site.info.fname = file.path(data.dir, paste(family, "_out_m.da.csv", sep = ""))
protein_list.fname = file.path(data.dir, paste(family, "_list.txt", sep = ""))

@@

##

z.RSD.exp = d$mean.z.RSD[d$dataset == "exp"]
z.RSD.strong = d$mean.z.RSD[d$dataset == "mut+sel"]
z.RSD.mut = d$mean.z.RSD[d$dataset == "mut"]

m.min.da.CM.ca = read.csv(file.path(data.dir, "min.da.CM.ca.csv", sep = ""))[, 2:4]

data.csv = data.frame(m.min.da.CM.ca[1:151, ], "mean.z.RSD.exp" = z.RSD.exp, "mean.z.RSD.strong" = z.RSD.strong, "mean.z.RSD.mut" = z.RSD.mut)

write.csv(data.csv, file.path(data.dir, "data.da.csv", sep = ""))

m.min.da.CM = m.min.da.CM.ca$min.da.CM[1:151]

data.plot = data.frame("d.exp.mut" = z.RSD.mut - z.RSD.exp, "d.exp.strong" = z.RSD.mut - z.RSD.strong, "m.min.da.CM" = m.min.da.CM)

r = round(cor(data.plot$d.exp.mut, data.plot$m.min.da.CM), 2)

ggplot(data.plot, aes(y = d.exp.mut, x = m.min.da.CM)) +
  geom_point()+
  geom_smooth(method = "lm") +
  geom_label(aes(x = 5, y = 2, label = paste("R =", as.character(r)))) +
    labs(y = "mean.z.RSD.mut - mean.z.RSD.exp", x = "min.da.CM")

r = round(cor(data.plot$d.exp.strong, data.plot$m.min.da.CM), 2)

ggplot(data.plot, aes(y = d.exp.strong, x = m.min.da.CM)) +
  geom_point()+
  geom_smooth(method = "lm") +
  geom_label(aes(x = 5, y = 0.5, label = paste("R =", as.character(r)))) +
    labs(y = "mean.z.RSD.strong - mean.z.RSD.exp", x = "min.da.CM")

##

m.min.da.ca = m.min.da.CM.ca$min.da.ca[1:151]

data.plot = data.frame("d.exp.mut" = z.RSD.mut - z.RSD.exp, "d.exp.strong" = z.RSD.strong - z.RSD.exp, "m.min.da.ca" = m.min.da.ca)

r = round(cor(data.plot$d.exp.mut, data.plot$m.min.da.ca), 2)

ggplot(data.plot, aes(y = d.exp.mut, x = m.min.da.ca)) +
  geom_point()+
  geom_smooth(method = "lm") +
  geom_label(aes(x = 5, y = 2, label = paste("R =", as.character(r)))) +
    labs(y = "mean.z.RSD.mut - mean.z.RSD.exp", x = "min.da.ca")

r = round(cor(data.plot$d.exp.strong, data.plot$m.min.da.ca), 2)

ggplot(data.plot, aes(y = d.exp.strong, x = m.min.da.ca)) +
  geom_point()+
  geom_smooth(method = "lm") +
  geom_label(aes(x = 5, y = 2, label = paste("R =", as.character(r)))) +
    labs(y = "mean.z.RSD.strong - mean.z.RSD.exp", x = "min.da.ca")

>>>>

---
title: "Structural Divergence Analysis"
author: "María Laura Marcos, Julian Echave"
date: "10 de septiembre de 2016"
output: html_document
---

@@

source(file.path(data.dir, "multiplot.R"))
source(file.path(data.dir, "my-functions.R")) 
```

```{r set_my_colors, eval = T}
myColors = c("blue", "darkgreen", "red", "red") 
names(myColors) <- c("exp", "mut", "strong", "mut+sel")
```
# Introduction
We study the evolutionary divergence of proteins using the LFENM and compare with experimental data.

```{r set_run_variables}
# significance factors
f95 = 1.96
f99 = 2.6
f999 = 3.3
```

@@

reference.fname = file.path(data.dir, paste(family, "_ref.txt", sep = ""))
protein_list.fname = file.path(data.dir, paste(family, "_list.txt", sep = ""))
site.info.fname = file.path(data.dir, paste(p.ref, "_m.da.csv", sep = ""))

@@

m.min.da.CM = read.csv(file.path(data.dir, "min.da.CM.csv", sep = ""))$x[1:151]

z.RSD.exp = d$mean.z.RSD[d$dataset == "exp"]
z.RSD.strong = d$mean.z.RSD[d$dataset == "strong"]
z.RSD.mut = d$mean.z.RSD[d$dataset == "mut"]

plot(y = z.RSD.exp-z.RSD.strong, x = m.min.da.CM)
abline(0,0, col = "red")
plot(y = (z.RSD.exp-z.RSD.mut), x = m.min.da.CM)
abline(0,0, col = "red")

### 2016-09-16 OUT/analysis-structure.Rmd
cambios 16/09/2016

---
title: "Structural Divergence Analysis"
author: "María Laura Marcos, Julian Echave"
date: "25 de julio de 2016"
output: html_document
---

@@

setwd("C:/Users/Usuario/Desktop/VariabilidadEstructuralProteica")

source("OUT/out_subset_CM/multiplot.R")
source("OUT/out_subset_CM/my-functions.R")
```

```{r set_my_colors, eval = T}
myColors = c("blue", "darkgreen", "red", "red")
names(myColors) <- c("exp", "mut", "strong", "mut+sel")

setwd("C:/Users/Usuario/Desktop/VariabilidadEstructuralProteica/OUT")

```
# Introduction
We study the evolutionary divergence of proteins using the LFENM and compare with experimental data.

```{r set_run_variables}
# Set options
family = "globins"
R0 = 7.5
enm = "ANM"

# significance factors
f95 = 1.96
f99 = 2.6
f999 = 3.3
data.dir = paste("out_subset_CM", sep = "")
```

```{r set_file_names}
## Input and pre-processing of data
# Set up input filenames

reference.fname = file.path(data.dir, paste(family, "_ref.txt", sep = ""))
site.info.fname = file.path(data.dir, paste(family, "_out_m.da.csv", sep = ""))
protein_list.fname = file.path(data.dir, paste(family, "_list.txt", sep = ""))

dri2.exp.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
Pn.exp.fname = file.path(data.dir, paste(family,"_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.exp.Pn.csv", sep = ""))
energy.exp.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.exp.va.csv", sep = ""))

dri2.strong.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
Pn.strong.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
energy.strong.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))

dri2.mut.fname = file.path(data.dir,paste(family, "_R0_7.5_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
Pn.mut.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_no.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
energy.mut.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_no.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))

@@

## read site information of reference protein
site.info = read.csv(site.info.fname, header = T, sep = ";")

@@

# dat.with.means and standard errors
d = ddply(dat,c("dataset","site","AA","shell"), function(x) {
                mean.z.RSD = mean(x$z.RSD, na.rm = T)
                ndata = sum(!is.na(x$z.RSD))
                se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(ndata)
                data.frame(mean.z.RSD, ndata, se.z.RSD)
})
#d$dataset = factor(d$dataset, levels = c("exp", "mut", "strong"))
d$label = as.character(d$site)
active.sites = d$site[d$shell == 0]

@@

ggplot(dat, aes(x = site, y = mean.z.RSD, col = dataset)) + geom_line() +
    geom_text(data = subset(dat, dataset == "exp" & mean.z.RSD < -.5), aes(x = site, y = mean.z.RSD, label = site), nudge_y = -.1, size = 2)

@@

>>>>

---
title: "Structural Divergence Analysis"
author: "María Laura Marcos, Julian Echave"
output: html_document
---

@@

source(file.path(data.dir, "multiplot.R"))
source(file.path(data.dir, "my-functions.R")) 
```

```{r set_my_colors, eval = T}
myColors = c("blue", "darkgreen", "red", "red") 
names(myColors) <- c("exp", "mut", "strong", "mut+sel")
```
# Introduction
We study the evolutionary divergence of proteins using the LFENM and compare with experimental data.

```{r set_run_variables}
# significance factors
f95 = 1.96
f99 = 2.6
f999 = 3.3
```

```{r set_file_names}
## input and pre-processing of data
# set up input filenames

reference.fname = file.path(data.dir, paste(family, "_ref.txt", sep = ""))
protein_list.fname = file.path(data.dir, paste(family, "_list.txt", sep = ""))
site.info.fname = file.path(data.dir, paste(p.ref, "_m.da.ca.csv", sep = ""))

dri2.exp.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
Pn.exp.fname = file.path(data.dir, paste(family,"_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.Pn.csv", sep = ""))
energy.exp.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.va.csv", sep = ""))

dri2.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
Pn.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
energy.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))

dri2.mut.fname = file.path(data.dir,paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
Pn.mut.fname = file.path(data.dir, paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
energy.mut.fname = file.path(data.dir, paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))

@@

## read site information of reference protein
site.info = read.csv(site.info.fname, header = T, sep = ",")[1:151, ]

@@

# dat.with.means and standard errors
d = ddply(dat,c("dataset","site","AA","shell"), function(x) {
                mean.z.RSD = mean(x$z.RSD, na.rm = T)
                ndata = sum(!is.na(x$z.RSD))
                se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(ndata)
                data.frame(mean.z.RSD, ndata, se.z.RSD)
})

m.min.da.CM = read.csv(file.path(data.dir, paste(p.ref, "_min.da.CM.ca.csv", sep = "")))

z.RSD.exp = d$mean.z.RSD[d$dataset == "exp"]
z.RSD.strong = d$mean.z.RSD[d$dataset == "mut+sel"]
z.RSD.mut = d$mean.z.RSD[d$dataset == "mut"]

plot(y = z.RSD.exp-z.RSD.strong, x = m.min.da.CM$min.da.ca[1:151])
plot(y = (z.RSD.exp-z.RSD.mut), x = m.min.da.CM$min.da.CM[1:151])

#d$dataset = factor(d$dataset, levels = c("exp", "mut", "strong"))
d$label = as.character(d$site)
active.sites = d$site[d$shell == 0]

@@

ggplot(dat, aes(x = site, y = mean.z.RSD, col = dataset)) + geom_line() +
    geom_text(data = subset(dat, dataset == "exp" & mean.z.RSD < -.5), aes(x = site, y = mean.z.RSD, label = site), nudge_y = -.1, size = 1.8)

@@

# Write pdb files for MSDi.

  pdb = ReadCA(reference.pdb.fname, chain.p.ref)$xyz

  mean.exp.z.RSD.pdb <- vec2resno(as.vector(dat.exp$mean.z.RSD), sort(rep(1:ncol(pdb),3)))
  write.pdb(xyz = c(pdb), b = mean.exp.z.RSD.pdb, file = paste(p.ref, "_exp.pdb", sep = ""))

  mean.mut.z.RSD.pdb <- vec2resno(as.vector(dat.mut$mean.z.RSD), sort(rep(1:ncol(pdb),3)))
  write.pdb(xyz = c(pdb), b = mean.mut.z.RSD.pdb, file = paste(p.ref, "_mut.pdb", sep = ""))

  mean.strong.z.RSD.pdb <- vec2resno(as.vector(dat.strong$mean.z.RSD), sort(rep(1:ncol(pdb),3)))
  write.pdb(xyz = c(pdb), b = mean.strong.z.RSD.pdb, file = paste(p.ref, "_strong.pdb", sep = ""))
```

### 2016-09-16 other_programs_files/MultipleReportAllBetasGlobins.Rmd
cambios 16/09/2016

# Set directories.
data.dir <- "DATA"
out.dir <- "OUT/out_subset_CM"

# p.ref.
n.sites.p.ref = 156

@@

# Information of sites.
gaps = c(18, 19, 51, 52, 53, 54, 55, 148, 149, 150, 151)
active = c(28, 29, 32, 64, 68, 93, 107)
heme = c(152, 153, 154, 155, 156)

@@

@@

    # Pn.
    m.exp.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.Pn.csv", sep = "")))[, 1:100]
    mean.exp.Pn = colMeans(m.exp.Pn)
    m.mean.exp.Pn[as.vector(all.betas == beta), 1:length(mean.exp.Pn)] = mean.exp.Pn
    n.prot = nrow(m.exp.Pn)

    # MSDi.
    m.exp.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.norm.dr.squarei.csv", sep = "")))

    m.exp.smooth.norm.dr.squarei = m.exp.smooth.norm.dr.squarei[-c(6, 7, 9, 29, 31), ] # Saqué proteínas que Julian no usó

    n.prot = nrow(m.exp.smooth.norm.dr.squarei)
    exp.smooth.norm.MSDi = colMeans(m.exp.smooth.norm.dr.squarei, na.rm = T)
    exp.smooth.norm.MSDi.sd = apply(m.exp.smooth.norm.dr.squarei, 2, sd, na.rm = T)/sqrt(no.gaps) * 1.96 # Ver si no hay que hacer sd dp

    exp.smooth.norm.MSDi.sd = exp.smooth.norm.MSDi.sd[!is.na(exp.smooth.norm.MSDi.sd)]

    exp.smooth.norm.MSDi = scale(sqrt(exp.smooth.norm.MSDi))[, 1]

    exp.smooth.norm.MSDi = exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)]

@@

    # Pn.
    m.theo.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.Pn.csv", sep = "")))[, 1:100]

@@

    # MSDi.
    m.theo.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.norm.dr.squarei.csv", sep = "")))

    theo.smooth.norm.MSDi = colMeans(m.theo.smooth.norm.dr.squarei, na.rm = T)

    MSDi.fit = scale(sqrt(theo.smooth.norm.MSDi))[, 1]

    MSDi.fit = MSDi.fit[1:length(exp.smooth.norm.MSDi)]

    ### COMPARE EXPERIMENTAL AND THEORETICAL ###
    MSDi.R2 = cor(exp.smooth.norm.MSDi, MSDi.fit) ^ 2

    MSDi.MSE = mean((MSDi.fit - exp.smooth.norm.MSDi) ^ 2)

    ### SAVE DATA IN MATRICES ###
    m.exp.MSDi[as.vector(all.betas == beta), ] = exp.smooth.norm.MSDi
    m.exp.MSDi.sd[as.vector(all.betas == beta), ] = exp.smooth.norm.MSDi.sd
    m.MSDi.fit[as.vector(all.betas == beta), ] = MSDi.fit
    m.MSDi.R2[as.vector(all.betas == beta), ] = MSDi.R2
    m.MSDi.MSE[as.vector(all.betas == beta), ] = MSDi.MSE

@@

    m.mean.exp.Pn[as.vector(all.betas == beta), 1:(length(mean.exp.Pn))] = mean.exp.Pn
    m.Pn.fit[as.vector(all.betas == beta), 1:(length(Pn.fit))] = Pn.fit
    m.Pn.R2[as.vector(all.betas == beta), ] = Pn.R2
    m.Pn.MSE[as.vector(all.betas == beta), ] = Pn.MSE

@@

    pdb <- read.pdb(pdbs.fname, ATOM.only = "TRUE")
    sel <- atom.select(pdb)
    b.factor <- pdb$atom$b
    site = as.numeric(pdb$atom[sel$atom, c("resno")])[1:1203]
    MSDi.fit.pdb <- vec2resno(as.vector(MSDi.fit[1:151]), site)
    exp.MSDi.pdb <- vec2resno(as.vector(exp.smooth.norm.MSDi[1:151]), site)
    b.factor.fit = b.factor
    b.factor.exp = b.factor

@@

    write.pdb(pdb = pdb, b = b.factor.exp, file = file.path(out.dir, paste(family, "_", p.ref, "_exp", ".pdb", sep = "")))
}

@@

MSDi.exp = m.exp.MSDi[1, 1:151]
MSDi.theo = m.MSDi.fit[1, 1:151]
MSDi.exp.sd = m.exp.MSDi.sd[1, 1:151]

@@

ggplot(data = data.MSDi, aes(x = sites)) + 
  geom_errorbar(aes(y = MSDi.exp, ymin = MSDi.exp - MSDi.exp.sd, ymax = MSDi.exp + MSDi.exp.sd), width = 0, col = gray(0.5)) +
  geom_line(aes(y = MSDi.theo, colour = "MSDi.theo"), col = "black") +
  geom_point(aes(y = MSDi.exp, colour = type), size = 1.5) + 
  ylab("MSDi strong selection")

@@

ggplot(data = data.MSDi, aes(x = sites)) + 
  geom_errorbar(aes(y = MSDi.exp, ymin = MSDi.exp - MSDi.exp.sd, ymax = MSDi.exp + MSDi.exp.sd), width = 0, col = gray(0.5)) +
  geom_line(aes(y = MSDi.theo, colour = "MSDi.theo"), col = "black") +
  geom_point(aes(y = MSDi.exp, colour = type), size = 1.5) + 
  ylab("MSDi medium selection")

@@

ggplot(data = data.MSDi, aes(x = sites)) + 
  geom_errorbar(aes(y = MSDi.exp, ymin = MSDi.exp - MSDi.exp.sd, ymax = MSDi.exp + MSDi.exp.sd), width = 0, col = gray(0.5)) +
  geom_line(aes(y = MSDi.theo, colour = "MSDi.theo"), col = "black") +
  geom_point(aes(y = MSDi.exp, colour = type), size = 1.5) + 
  ylab("MSDi weak selection")

@@

ggplot(data = data.MSDi, aes(x = sites)) + 
  geom_errorbar(aes(y = MSDi.exp, ymin = MSDi.exp - MSDi.exp.sd, ymax = MSDi.exp + MSDi.exp.sd), width = 0, col = gray(0.5)) +
  geom_line(aes(y = MSDi.theo, colour = "MSDi.theo"), col = "black") +
  geom_point(aes(y = MSDi.exp, colour = type), size = 1.5) + 
  ylab("MSDi no selection") +
```

>>>>

# Set directories.
data.dir <- "DATA"
out.dir <- "OUT"

# p.ref.
n.sites.p.ref = read.csv(file.path(out.dir, paste(family, "_out_m.n.sites.p.ref.csv", sep = "")))$V1[1]

@@

@@

    gaps = c(18, 19, 47, 48, 49, 50, 51, 52, 53, 54, 55, 148, 149, 150, 151)
    active = c(28, 29, 32, 64, 68, 93, 107)

@@

    m.exp.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.Pn.csv", sep = "")))[, 1:100]
    n.prot = nrow(m.exp.Pn)

    mean.exp.Pn = colMeans(m.exp.Pn)
    exp.Pn.sd = apply(m.exp.Pn, 2, sd, na.rm = T)/sqrt(n.prot) * 1.96
    m.mean.exp.Pn[as.vector(all.betas == beta), 1:length(mean.exp.Pn)] = mean.exp.Pn

    m.exp.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.smooth.norm.dr.squarei.csv", sep = "")))
    no.gaps = colSums(matrix(as.numeric(!is.na(m.exp.smooth.norm.dr.squarei)), nrow = n.prot))
    exp.smooth.norm.MSDi = colMeans(m.exp.smooth.norm.dr.squarei, na.rm = T )
    exp.smooth.norm.MSDi.sd = apply(m.exp.smooth.norm.dr.squarei, 2, sd, na.rm = T)/sqrt(no.gaps) * 1.96

@@

    m.theo.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.Pn.csv", sep = "")))[, 1:100]

    m.theo.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.norm.dr.squarei.csv", sep = "")))

    theo.smooth.norm.MSDi = colMeans(m.theo.smooth.norm.dr.squarei, na.rm = T )

@@

    fit = lm(exp.smooth.norm.MSDi ~ theo.smooth.norm.MSDi )
    MSDi.fit = fitted.values(fit)
    MSDi.R2 = cor(exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)], MSDi.fit) ^ 2 
    MSDi.MSE = mean((MSDi.fit - exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)]) ^ 2)
    exp.smooth.norm.MSDi = exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)]

    m.MSDi.fit[as.vector(all.betas == beta), ] = MSDi.fit
    m.MSDi.R2[as.vector(all.betas == beta), ] = MSDi.R2
    m.MSDi.MSE[as.vector(all.betas == beta), ] = MSDi.MSE
    m.exp.MSDi[as.vector(all.betas == beta), ] = exp.smooth.norm.MSDi
    m.exp.MSDi.sd[as.vector(all.betas == beta), ] = exp.smooth.norm.MSDi.sd[!is.na(exp.smooth.norm.MSDi.sd)]

@@

  m.Pn.fit[as.vector(all.betas == beta), 1:(length(Pn.fit))] = Pn.fit
  m.Pn.R2[as.vector(all.betas == beta), ] = Pn.R2
  m.Pn.MSE[as.vector(all.betas == beta), ] = Pn.MSE
  m.mean.exp.Pn[as.vector(all.betas == beta), 1:(length(mean.exp.Pn))] = mean.exp.Pn
  m.exp.Pn.sd[as.vector(all.betas == beta), 1:(length(exp.Pn.sd))] = exp.Pn.sd

@@

  pdb <- read.pdb(pdbs.fname, ATOM.only = T)
  sel <- atom.select(pdb)
  b.factor <- pdb$atom$b
  site = as.numeric(pdb$atom[sel$atom, c("resno")])[1:1203]
  MSDi.fit.pdb <- vec2resno(as.vector(MSDi.fit), site)
  exp.MSDi.pdb <- vec2resno(as.vector(exp.smooth.norm.MSDi), site)
  b.factor.fit = b.factor
  b.factor.exp = b.factor

@@

  write.pdb(pdb = pdb, b = b.factor.exp, file = file.path(out.dir, paste(family, "_", p.ref, "_exp", ".pdb", sep = "")))

}

@@

MSDi.exp = m.exp.MSDi[1, ]
MSDi.theo = m.MSDi.fit[1, ]
MSDi.exp.sd = m.exp.MSDi.sd[1, ]

@@

ggplot(data = data.MSDi, aes(x = sites)) + 
  geom_errorbar(aes(y = MSDi.exp, ymin = MSDi.exp - MSDi.exp.sd, ymax = MSDi.exp + MSDi.exp.sd), width = 0, col = gray(0.5)) +
  geom_line(aes(y = MSDi.theo, colour = "MSDi.theo"), col = "black") +
  geom_point(aes(y = MSDi.exp, colour = type), size = 1.5) + 
  ylab("MSDi strong selection") +
  scale_color_manual(values=c("green", "yellow", "red", "black"))

@@

ggplot(data = data.MSDi, aes(x = sites)) + 
  geom_errorbar(aes(y = MSDi.exp, ymin = MSDi.exp - MSDi.exp.sd, ymax = MSDi.exp + MSDi.exp.sd), width = 0, col = gray(0.5)) +
  geom_line(aes(y = MSDi.theo, colour = "MSDi.theo"), col = "black") +
  geom_point(aes(y = MSDi.exp, colour = type), size = 1.5) + 
  ylab("MSDi medium selection") +
  scale_color_manual(values=c("green", "yellow", "red", "black"))

@@

ggplot(data = data.MSDi, aes(x = sites)) + 
  geom_errorbar(aes(y = MSDi.exp, ymin = MSDi.exp - MSDi.exp.sd, ymax = MSDi.exp + MSDi.exp.sd), width = 0, col = gray(0.5)) +
  geom_line(aes(y = MSDi.theo, colour = "MSDi.theo"), col = "black") +
  geom_point(aes(y = MSDi.exp, colour = type), size = 1.5) + 
  ylab("MSDi weak selection") +
  scale_color_manual(values=c("green", "yellow", "red", "black"))

@@

ggplot(data = data.MSDi, aes(x = sites)) + 
  geom_errorbar(aes(y = MSDi.exp, ymin = MSDi.exp - MSDi.exp.sd, ymax = MSDi.exp + MSDi.exp.sd), width = 0, col = gray(0.5)) +
  geom_line(aes(y = MSDi.theo, colour = "MSDi.theo"), col = "black") +
  geom_point(aes(y = MSDi.exp, colour = type), size = 1.5) + 
  ylab("MSDi no selection") +
  scale_color_manual(values=c("green", "yellow", "red", "black"))
